Turnover of species and interactions

### 2018-10-29 paper/data-exploration/turnover.Rmd
Explore how number of focal species changes with the thershold

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300)
```

@@

```{r, eval = F}
selected <- int_rank %>%
  dplyr::select(pla_name, pol_name, n_loc, focal) %>% 
  tidyr::gather("guild", "sp_name", pla_name, pol_name) %>% 
  dplyr::mutate(guild = substr(guild, 1,3),
                focal_int = TRUE) %>% 
  dplyr::group_by(guild, sp_name) %>%
  dplyr::summarise(n_loc_int = mean(n_loc), 
                   n_loc_max = max(n_loc),
                   focal_int = any(focal), 
                   n = n()) %>% 
  dplyr::distinct() %>%
  dplyr::left_join(sp_rank)

selected %>% 
  # dplyr::filter(focal, focal_int) %>%
  ggplot(aes(x = n_loc, y = n_loc_int)) +
  geom_point(aes(colour = log(n))) +
  geom_label_repel(data = dplyr::filter(selected, focal, focal_int),
                  aes(label = sp_name), size = 3, fontface =  "italic",
                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) 
```

@@

@@

sp_deg_rank %>%
  dplyr::group_by() %>%
  humanize() %>%
  ggplot(aes(x = deg, y = n_loc)) +
  geom_vline(data = median_deg, aes(xintercept = deg, colour = selected), 
             size = 0.25, 
             linetype = 2) +
  geom_text(data = median_deg, 
            aes(y = 20, 
                label = paste("median", guild, "-", deg), 
                color = selected),
            nudge_x = -0.05,
            angle = 90, 
            size = 3) +
  geom_point(aes(colour = selected, fill = selected, shape = guild)) +
  geom_label_repel(data = dplyr::filter(sp_deg_rank, selected), 
                  aes(label = sp_name), size = 3, fontface =  "italic",
                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
  scale_x_log10() +
  # scale_y_log10() +
  scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(21, 24)) +
  guides(color = guide_legend("focal species"), 
         fill = guide_legend("focal species")) +
  theme_bw() +
  theme(legend.position = c(0.02,0.98), 
        legend.justification = c(0,1), 
        legend.box = "horizontal") +
  labs(title = "species degree vs. number of locations", 
       subtitle = "there are 16 focal species, mostly generalist pollinators",
       caption = "focal species are those that have the same interaction in >= 3 locations and are present >= 5 locations", 
       y = "# locations", 
       x = "species degree")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16)
```

@@

Combining these two thresholds

 * Only species with interactions that were sampled in three locations or more
 * Only species sampled in 5 locations or more

we have 16 focal species for which enough interaction data could be obtained from Bascompte's Web of Life. Four plants and 12 pollinators.

Now let's have a little look at how these numbers depend on the chosen threshold.

```{r}
drake::loadd(focal_species_options)

focal_species_options %>%
  dplyr::group_by(int_threshold, sp_threshold, guild) %>%
  dplyr::summarise(n = n()) %>% 
  dplyr::group_by(int_threshold, sp_threshold) %>%
  dplyr::mutate(n_total = sum(n), 
                label = paste(format(n_total, big.mark = ","), "spp."),
                label2 = paste(format(n, big.mark = ","), guild), 
                label2 = paste(label2, collapse = "+")) %>%
  dplyr::select(-guild) %>%
  dplyr::distinct() %>%
  humanize() %>%
  ggplot(aes(x = int_threshold, y = sp_threshold)) +
  geom_tile(aes(fill = n_total)) +
  geom_text(aes(label = label), 
            size = 3, 
            fontface = "bold", 
            nudge_y = 0.2, 
            color = "white") +
  geom_text(aes(label = label2), 
            size = 3, 
            nudge_y = -0.2, 
            color = "white") +
  geom_tile(aes(x = 3, y = 5), fill = NA, colour = "white", linetype = 2) +
  scale_fill_continuous(trans = "log10") +
  coord_cartesian(ylim = c(1,10)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(breaks = 1:10) +
  theme_bw() +
  labs(title = "number of focal species", 
       subtitle = "number of plants and pollinators using different thresholds", 
       x = "repeated interaction threshold", 
       y = "species location threshold", 
       fill = "# spp.", 
       caption = "dashed box indicate thresholds used here")
```

@@

Let's have a closer look at the chosen thresholds of 5 and 3. 
I'm a bit worried that we're only selecting super generalist species and hence results might be biased. 
We can see that indeed the overall species degree of the focal species is considerably larger than that of non-focal. We have still a decent range between 6 for *Fuchia regia* and like 400 for *Apis melifera*.

@@

sp_deg_rank %>%
  dplyr::group_by() %>%
  humanize() %>%
  ggplot(aes(x = deg, y = n_loc)) +
  geom_vline(data = median_deg, aes(xintercept = deg, colour = selected), 
             size = 0.25, 
             linetype = 2) +
  geom_text(data = median_deg, 
            aes(y = 20, 
                label = paste("median", guild, "-", deg), 
                color = selected),
            nudge_x = -0.05,
            angle = 90, 
            size = 3) +
  geom_point(aes(colour = selected, fill = selected, shape = guild)) +
  geom_label_repel(data = dplyr::filter(sp_deg_rank, selected), 
                  aes(label = sp_name), size = 3, fontface =  "italic",
                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
  scale_x_log10() +
  # scale_y_log10() +
  scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(21, 24)) +
  guides(color = guide_legend("focal species"), 
         fill = guide_legend("focal species")) +
  theme_bw() +
  theme(legend.position = c(0.02,0.98), 
        legend.justification = c(0,1), 
        legend.box = "horizontal", 
        legend.direction = "horizontal") +
  labs(title = "species degree vs. number of locations", 
       subtitle = "there are 16 focal species, mostly generalist pollinators",
       caption = "focal species are those that have the same interaction in >= 3 locations and are present >= 5 locations", 
       y = "# locations", 
       x = "species degree")
```
